Contextuality and the Born rule in fuzzy quantum theories

### 2017-04-22 prop_letter.tex
prop_letter.tex \paragraph{Expectation Values for Quantum IVPMs} Updating...

In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
we have
\begin{equation}
\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\subsetneq\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
\end{equation}
because the precision is easily be lost when applying arithmetic operations.
In general, when $\bar{\mu}$ is convex, we have 
\begin{equation}
\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{.}
\end{equation}

@@

It asserts that there exists no function~$v$ assigning definite
values to all observables such that for any sequence of commuting
observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
 &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).
\end{eqnarray}
\end{subequations}Suppose that there is a function~$v$ satisfying
these two properties, it must send an observable to its eigenvalues
so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
\end{aligned}
\label{eq:MerminSquare-values}
\end{equation}
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).

>>>>

In contrast to the usual identity~$\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\rho}=\expval{\mathbf{O}_{1}}_{\rho}+\expval{\mathbf{O}_{2}}_{\rho}$,
we have
\begin{equation}
\expval{\mathbb{0}}_{\bar{\mu}_{1}}=\left[0,0\right]\subsetneq\left[-2,2\right]=\expval{\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}+\expval{-\sigma_{\mathrm{z}}}_{\bar{\mu}_{1}}
\end{equation}
because the precision is easily be lost when applying arithmetic operations.
In general, when $\bar{\mu}$ is convex, we have 
\begin{equation}
\expval{\mathbf{O}_{1}+\mathbf{O}_{2}}_{\bar{\mu}}\subseteq\expval{\mathbf{O}_{1}}_{\bar{\mu}}+\expval{\mathbf{O}_{2}}_{\bar{\mu}}\textrm{ ,}
\end{equation}
for commuting $\mathbf{O}_{1}$ and $\mathbf{O}_{2}$.

\yutsung{{Even if we have expectation value of }an observable, I
don't know how to reason Mermin square~(\ref{eq:MerminSquare}) directly
with quantum IVPM so far. The problem is the valuation function~$v$
is not an expectation value. Since the corresponding of Eq.~(\ref{eq:deterministic-product}),
$E\left[XY\right]=E\left[X\right]E\left[Y\right]$, doesn't hold for
expectation value except $X$ and $Y$ are uncorrelated or even independent~\cite{rohatgi2011introduction}.}

@@

It asserts that there exists no function~$v$ assigning definite
values to all observables such that for any sequence of commuting
observables, $\left\{ \mathbf{O}_{j}\right\} $,\begin{subequations}\label{eq:Kochen-Specker-Rules}
\begin{eqnarray}
 &  & \sum_{j}v\left(\mathbf{O}_{j}\right)=v\left(\sum_{j}\mathbf{O}_{j}\right)\textrm{ and}\\
 &  & \prod_{j}v\left(\mathbf{O}_{j}\right)=v\left(\prod_{j}\mathbf{O}_{j}\right).\label{eq:deterministic-product}
\end{eqnarray}
\end{subequations}Suppose that there is a function~$v$ satisfying
these two properties, it must send an observable to its eigenvalues
so that the following observables~\cite{Mermin1990Simple,peres1995quantum}:
\begin{equation}
\begin{aligned}\mathbb{1} & \otimes\sigma_{z} & \sigma_{z} & \otimes\mathbb{1} & \sigma_{z} & \otimes\sigma_{z}\\
\sigma_{x} & \otimes\mathbb{1} & \mathbb{1} & \otimes\sigma_{x} & \sigma_{x} & \otimes\sigma_{x}\\
\sigma_{x} & \otimes\sigma_{z} & \sigma_{z} & \otimes\sigma_{x} & \sigma_{y} & \otimes\sigma_{y}
\end{aligned}
\label{eq:MerminSquare}
\end{equation}
must be sent to $1$ or $-1$. In each row and column, operators commutes,
and each operator is the product of the two others, except in the
third column $\left(\sigma_{z}\otimes\sigma_{z}\right)\left(\sigma_{x}\otimes\sigma_{x}\right)=-\sigma_{y}\otimes\sigma_{y}$.
Therefore, it is clear impossible to find a function~$v$ such that
\begin{equation}
\begin{aligned}v(\mathbb{1} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\mathbb{1}) & v(\sigma_{z} & \otimes\sigma_{z})\\
v(\sigma_{x} & \otimes\mathbb{1}) & v(\mathbb{1} & \otimes\sigma_{x}) & v(\sigma_{x} & \otimes\sigma_{x})\\
v(\sigma_{x} & \otimes\sigma_{z}) & v(\sigma_{z} & \otimes\sigma_{x}) & v(\sigma_{y} & \otimes\sigma_{y})
\end{aligned}
\label{eq:MerminSquare-values}
\end{equation}
satisfying Eq.~(\ref{eq:Kochen-Specker-Rules}).
